Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-07 main.tex
WIP conclusion: role of teachers

>>>>

No surprinsingly, the role of the robot \textit{vis-à-vis} the teacher has also
been questionned (including an angry email from one teacher: ``You want to
replace us!''): as we see it, the role of the robot within the classroom (or at
the therapist's surgery) does not infringe upon the role of the adult (teacher
or therapist).  The core of the \emph{learning by teaching} paradigm relies on
the child becoming the teacher of an underperforming pupil (the robot): from
that perspective, the robot does not replace the teacher, on the contrary. It
plays a different role in the classroom, which happen to be novel as well: the
robot is the \emph{least} performing student, and however a very patient, always
eager to improve, one.

The importance of the adult is further supported by our experiments: even with
an autonomous, nominally performing robot, to put the teacher's clothes on
remains (expectedly) difficult for 5-6 years old children, and during the
experiments we conducted, the adult always played a key role at prompting the
child to give feedback to the robot or to go to the next letter or word.  At a
higher orchestration level (and as reported in the two case studies with Diego
and Henry), the educational scenarios were also always designed and monitored by
the adults.

We initially envisionned the CoWriter system to be run in the back of a
classroom with one child: this would have allowed an individual, face-to-face
remediation approach, not otherwise tractable for a teacher with 20 pupils.
This is unlikely to happen. In our experience, the teacher keeps such an
important role that the interaction and the learning would hardly occur if the
child is left alone (or even semi-alone). At the end, we can reassure teachers:
robots are not going to replace them any time soon.
